Modeling Liver with Glisson's Capsule in Real-Time Medical Simulations

### 2013-05-31 Doc/Vrst2013/vrst2013.tex
ADD: figure
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@586 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

@@

In the second step, we employed the simulation to reproduce the displacements values obtained via simulation in~\cite{Hollenstein2006,Nava2008}.
Whereas the simulation in the referenced work was done on a mesh composed of tetrahedral elements for both the parenchyma 
and the capsule, we modelled the capsule using the triangular elements as shown in section~\ref{}.

>>>>

\begin{figure}
  \centering
  \includegraphics[height=3.5cm]{displacement.pdf}
  \caption{\label{fig-aspiration1} The }
\end{figure}

@@

In the second step, we employed the simulation to reproduce the displacements values obtained via simulation in~\cite{Hollenstein2006,Nava2008}.
Whereas the simulation in the referenced work was done on a mesh composed of tetrahedral elements for both the parenchyma 
and the capsule, we modelled the capsule using the triangular elements as shown in section~\ref{ss:capsuleModel}.
